Predicting instabilities of a tuneable ring laser with an iterative map model

### 2021-05-31 Papers/Journal/Tuneable_Lasers.tex
Extended paragraph to talk about the energy variation

\begin{figure*}[tbp]
	\centering
	\begin{subfigure}{\columnwidth}
		\centering
		\includegraphics{Figures/Chirp}
		\caption{Chirp.}
		\label{fig:chirp}
	\end{subfigure} %
	\begin{subfigure}{\columnwidth}
		\centering
		\includegraphics{Figures/FT}
		\caption{Fourier transform.}
		\label{fig:ft}
	\end{subfigure}
	\caption{Chirp and Fourier transform at equilibrium (after 500 round trips) initiated by \eqref{eq:nlA0} for three values of $b$, the nonlinearity parameter ($a = 8 \times 10^3$, $h = 0.04$, $s = 0.2$, and $E_0 = 0.1$).}
	\label{fig:chirpft}
\end{figure*}

@@

Also of interest is the energy of the pulse at equilibrium, which we compute numerically by \eqref{eq:energy}. Given our ordering of the components, we compute the energy of the pulse immediately before passing through the optical coupler. Thus, the energy of each pulse emitted by the laser is $(1 - h^2) E$, and $h^2 E$ remains in the cavity. We plot the energy in the $s$--$b$ plane in Fig.~\ref{fig:energy}. Unsurprisingly, we find the same sharp boundary as we saw in Fig.~\ref{fig:error}. In the unstable region (upper-left) the energy is small. The pulse is not able to foster prominent modes in this region, and is unsustainable, thus, the intensity is low across the entire pulse. In the stable region (lower-right) we find the energy decays smoothly as both $b$ and $s$ increase, with the contours being hyperbolic-esque. As $s$ increases, the tails of the pulse increase in length due to the dispersion, and more energy is lost due to modulation. As $b$ increases, our choice of modulation function helps suppress the additional frequencies generated by SPM, ensuring the pulse remains band-limited. We find a more energetic laser requires weaker dispersion, however, the nonlinearity must be correspondingly low, otherwise modulation instability will destroy the pulse. Moreover, the maximum energy, which occurs in the limit where both $s$ and $b$ go to zero, is 2.5487. With our choice of parameters, \eqref{eq:maxenergy} predicts an equilibrium energy of 2.5535 at the origin, confirming the usefulness of the approximation.

>>>>

\begin{figure*}[tbp]
	\centering
	\begin{subfigure}{\columnwidth}
		\centering
		\includegraphics{Figures/Chirp}
		\caption{Chirp.}
		\label{fig:chirp}
	\end{subfigure} \hfill
	\begin{subfigure}{\columnwidth}
		\centering
		\includegraphics{Figures/FT}
		\caption{Fourier transform.}
		\label{fig:ft}
	\end{subfigure}
	\caption{Chirp and Fourier transform at equilibrium (after 500 round trips) initiated by \eqref{eq:nlA0} for three values of $b$, the nonlinearity parameter ($a = 8 \times 10^3$, $h = 0.04$, $s = 0.2$, and $E_0 = 0.1$).}
	\label{fig:chirpft}
\end{figure*}

@@

Also of interest is the energy of the pulse at equilibrium, which we compute numerically by \eqref{eq:energy}. Given our ordering of the components, we compute the energy of the pulse immediately before passing through the optical coupler. Thus, the energy of each pulse emitted by the laser is $(1 - h^2) E$, and $h^2 E$ remains in the cavity. We plot the energy in the $s$--$b$ plane in Fig.~\ref{fig:energy}. Unsurprisingly, we find the same sharp boundary as we saw in Fig.~\ref{fig:error}. In the unstable region (upper-left) the energy is small. The pulse is not able to foster prominent modes in this region, and is unsustainable, thus, the intensity is low across the entire pulse. In the stable region (lower-right) we find the energy decays smoothly as both $b$ and $s$ increase, with the contours being hyperbolic-esque. As $s$ increases, the tails of the pulse increase in length due to the dispersion, and more energy is lost due to modulation. As $b$ increases, our choice of modulation function helps suppress the additional frequencies generated by SPM, ensuring the pulse remains band-limited. We find a more energetic laser requires weaker dispersion, however, the nonlinearity must be correspondingly low, otherwise modulation instability will destroy the pulse. Moreover, the maximum energy, which occurs in the limit where both $s$ and $b$ go to zero, is 2.5487. With our choice of parameters, \eqref{eq:maxenergy} predicts an equilibrium energy of 2.5535 at the origin, confirming the usefulness of the approximation. Moreover, we show in Fig. \ref{fig:energytime} the energy variation of four pulses during the 500 round trips. In particular, we plot two pulses in the stable region (purple and blue) and two pulses in the unstable region (green and red). Each of the pulses, again, has an initial energy of $E_0 = 0.1$, and after about a dozen round trips the energy is approximately 1.25 in the case of the $s = 0.35$, $b = 6.0$, and approximately 2 in the other three cases. The two examples in the stable region quickly reach equilibrium, and their energy remains constant for the remaining round trips. However, for the examples in the unstable region the pulses lose a considerable amount of their energy and the pulse begins to degrade. The energy of the pulses varies by up to 25\% between consecutive round trips. A pulse in the unstable region undergoes large transformations with each round trip leading to the error we saw in Fig. \ref{fig:error}, as well as the energy variation in Fig. \ref{fig:energytime}.

\begin{figure}[tbp]
	\centering
	\includegraphics{Figures/EnergyTime}
	\caption{Energy of four pulses during the first 500 round trips ($a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$).}
	\label{fig:energytime}
\end{figure}
